R Notebook

### 2017-03-14 manuscript/important_references.Rmd

#Various factoids
---------------------
On North American climate
There has been an increase in mean temperature in North America since the 1980's (pg. 90, fig 2.7) 
Redmond, Kelly T., and John T. Abatzoglou. "Current climate and recent trends." Climate Change in North America. Springer International Publishing, 2014. 53-94.

@@

#Forcasting
People should do a better job at forecasting.
Evans, M. R., Norris, K. J. & Benton, T. G. Predictive ecology: systems approaches. Philos. Trans. R. Soc. B Biol. Sci. 367, 163–169 (2012).
Houlahan, J. E. The priority of prediction in ecological understanding. Oikos (2016). doi:10.1111/oik.03726
Petchey, O. L. et al. The ecological forecast horizon, and examples of its uses and determinants. Ecol. Lett. 18, 597–611 (2015).

#SDM references

@@

>>>>

## Various factoids

#### On North American climate  
There has been an increase in mean temperature in North America since the 1980's (pg. 90, fig 2.7)   
Redmond, Kelly T., and John T. Abatzoglou. "Current climate and recent trends." Climate Change in North America. Springer International Publishing, 2014. 53-94.

@@

-------------------------------
#### Biodiversity is an important thing to consider   
Cardinale, Bradley J., et al. "Biodiversity loss and its impact on humanity." Nature 486.7401 (2012): 59-67.

## Forcasting
#### People should do a better job at forecasting.  
Evans, M. R., Norris, K. J. & Benton, T. G. Predictive ecology: systems approaches. Philos. Trans. R. Soc. B Biol. Sci. 367, 163–169 (2012).  
Houlahan, J. E. The priority of prediction in ecological understanding. Oikos (2016). doi:10.1111/oik.03726  
Petchey, O. L. et al. The ecological forecast horizon, and examples of its uses and determinants. Ecol. Lett. 18, 597–611 (2015).

## SDM references

@@

## Bird ecology
Renfrew, R. B., Kim, D., Perlut, N., Smith, J., Fox, J. and Marra, P. P. (2013), Phenological matching across hemispheres in a long-distance migratory bird. Diversity Distrib., 19: 1008–1019. doi:10.1111/ddi.12080
Stephen Mayor, a postdoc with Rob Guralnick, also has unpublished work looking at migration/ndvi patterns for all north american birds.
